%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[margin]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here
%\topmargin=-0.5in
%\bottommargin=-0.5in
\oddsidemargin -.3in
\evensidemargin -.3in
%\textwidth=6.0in
%\itemsep=0in
%\parsep=0in
%\setlength{textheight}{674pt}
\textheight 9.5in

\usepackage{natbib}
\usepackage{bibentry}
\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above
\usepackage{hyperref}
\usepackage{enumitem}

\setlength{\textwidth}{5.55in} % Text width of the document

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.3\hoffset\centerline{\LARGE \bf Jiang,\ Puping (Phil)} % Your name at the top

\moveleft\hoffset\vbox{\hrule width 7in height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'

%\moveleft.3\hoffset\centerline{Campus Box 1156, One Brookings Drive} % Your address
%\moveleft.3\hoffset\centerline{St. Louis, MO, 63130}
\moveleft.3\hoffset\centerline{jiang.p@wustl.edu}

%----------------------------------------------------------------------------------------

\begin{resume}

%% comment out the \nofile in the res.cls files to output the .aux file.
%    \bibliographystyle{plain}
%    \nobibliography{Myref}

%----------------------------------------------------------------------------------------
%	OBJECTIVE SECTION
%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

    \section{\textbf{EDUCATION}}
    {\bf Olin Business School, Washington University in St. Louis} \hfill {\em 08/2016-05/2022} \\ 
    -- Ph.D. in {\it Supply Chain, Operations, and Technology} \\
    ~
    \\
    {\bf University of Science and Technology of China, SFGY} \hfill {\em 09/2012-06/2016} \\ 
    -- B.S. in {\it Statistics}\\

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

    \section{\textbf{ACADEMIC POSITION}}
    {\bf Antai College of Economics and Management, Shanghai Jiao Tong University} \\ 
    -- Assistant Professor of Management Science \hfill {\em 08/2022-Current}\\

%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------
%\bigskip
    \section{RESEARCH INTERESTS} 
    Data-Driven Revenue Management, Platform Economics, Interface of Operations, Risk Management and Finance.

%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\section{JOURNAL PUBLICATIONS}
 %\itemsep -2pt % Reduce space between items
\begin{enumerate}[leftmargin=*]
    \item %\href{https://pubsonline.informs.org/doi/abs/10.1287/mnsc.2022.4440?casa_token=br5-nMm53OIAAAAA:nQxcEPswA7DUJZgJ1CZsL0DModEzd-a-1Y5zOh68ebSQo1LU177cocuRpaC3BXYQcoELLTilwzPY}{\bibentry{dong2022impact}} 
        \href{https://pubsonline.informs.org/doi/abs/10.1287/mnsc.2022.4440?casa_token=br5-nMm53OIAAAAA:nQxcEPswA7DUJZgJ1CZsL0DModEzd-a-1Y5zOh68ebSQo1LU177cocuRpaC3BXYQcoELLTilwzPY}{\textbf{Impact of Traceability Technology Adoption in Food Supply Chain Networks.}} {\it Management Science}, 2023 (with {\it Lingxiu Dong} and {\it Fasheng Xu})
        \begin{itemize}
            \item[--] {\it Tied Winner, 2020 PITM Best Student Paper Competition, POMS}
            \item[--] {\it Previously titled ``Blockchain Adoption for Traceability in Food Supply Chain Networks''}
        \end{itemize}
    \item \href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=3909033}{\textbf{Display Optimization Under the Multinomial Logit Choice Model: Balancing Revenue and Customer Satisfaction.}} {\it Production and Operations Management}, 2024 (with {\it Jake Feldman})
\end{enumerate}


    \section{WORKING PAPERS}
 %\itemsep -2pt % Reduce space between items
    \begin{enumerate}[resume,leftmargin=*]
        \item \href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=3936170}{\textbf{Vertical Information Sharing in the Presence of Investment Shocks: When May It Happen?}} (with {\it Panos Kouvelis}), \textit{Under review}.
        \item \href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=4815339}{\textbf{Data-Driven Asset Selling.}} (with {\it Lingxiu Dong}), \textit{Conditionally accepted by Production and Operations Management}
            \begin{itemize}
                \item[--] {\it Finalist, 2022 Jeff McGill Student Paper Award, INFORMS RMP Section}
            \end{itemize}
        \item \textbf{Online Optimization in Asset Selling Platforms.} (with {\it Ren\'{e} Caldentey} and {\it Lingxiu Dong}), \textit{To be submitted}.
        \item \textbf{Simple Delay-Oblivious Policies Are Robust: Overbooking with Delayed Purchases.} (with {\it Yiding Feng} and {\it Wei Tang}), \textit{Under review}.
        \item \textbf{Short-term Pain for Long-term Gain: An Online Learning Perspective.} (with {\it Wei Tang}), \textit{Under review}.
    \end{enumerate}


    %\section{WORK IN PROGRESS}
    %%\itemsep -2pt % Reduce space between items
    %\begin{enumerate}[resume,leftmargin=*]
    %\end{enumerate}



%----------------------------------------------------------------------------------------
%	COMMUNITY SERVICE SECTION
%---------------------------------------------------------------------------------------- 

\section{CONFERENCE AND SEMINAR PRESENTATIONS}
 %\itemsep -2pt % Reduce space between items
\begin{itemize}[leftmargin=*]
    \item INFORMS Annual Meeting, Seattle \hfill 10/2024
    \item INFORMS RMP Conference, Los Angeles \hfill 07/2024
    \item MSOM International Conference, Minneapolis \hfill 07/2024
    \item INFORMS Annual Meeting, Phoenix \hfill 10/2023
    \item INFORMS RMP Conference, Virtual \hfill 06/2022
    \item POMS Annual Conference, Virtual \hfill 05/2022
    \item INFORMS RMP Conference, Virtual \hfill 06/2021
    \item MSOM International Conference, Virtual \hfill 06/2021
    \item POMS Annual Conference, Virtual \hfill 05/2021
    \item INFORMS Virtual Annual Meeting \hfill 11/2020
    \item INFORMS Annual Meeting, Seattle \hfill 10/2019
    \item MSOM International Conference, Singapore \hfill 07/2019
    \item POMS Annual Conference, Washington DC \hfill 05/2019
\end{itemize}

\section{TEACHING}
Instructor (Antai, SJTU)
\begin{itemize}
    \item Online Optimization and Learning I \& II ({\it PhD: FL, SP 2024})
    \item Simulations for Management ({\it Undergraduate: FL 2022})
\end{itemize}
Teaching Assistant (Olin, WUSTL)
\begin{itemize}
    \item Inventory \& Supply-Chain Mgt. Theory \& Research ({\it PhD Core: SP 2019})
    \item Stochastic Models for Production and Service Systems ({\it PhD Core: SP 2019})
    \item Theory and Research Methods in Inventory and Supply Chain Management ({\it PhD Core: FL 2019})
    \item Intro to Python and Data Science ({\it MSSCM, MSCA Core: FL 2018, FL 2019})		
    \item Introduction to Revenue Management ({\it MSSCA Core: FL 2020, FL 2021})
    \item Operations Management ({\it MBA Core: 2017, 2018})
    \item Prescriptive Analytics ({\it MSSCM Core: FL 2018, FL 2019, FL 2020})		
    \item Supply Chain Management ({\it Undergraduate: SP 2019})
\end{itemize}

%----------------------------------------------------------------------------------------
%	EXTRA-CURRICULAR ACTIVITIES SECTION
%----------------------------------------------------------------------------------------

\section{AWARDS \& HONORS} 
    Finalist, 2022 Jeff McGill Student Paper Award\\
    Tied Winner, 2020 PITM Best Student Paper Competition, POMS\\
    2020 Moog Scholar Award, Olin Business School, WUSTL\\
    2019 Moog Scholar Award, Olin Business School, WUSTL\\

\section{CONSULTING}
    Boeing Center, WUSTL
    \begin{itemize}
        \item[--]Edward Jones: Contractor ROI, Spring, 2018
            \begin{itemize}
                \item We use empirical tools to provide insights into sourcing strategy ROI on contractors and identify the preferred cases to use contractors.
            \end{itemize}	
        \item[--]MilliporeSigma: Identifying Investment Opportunities through Online Customer Analytics, Fall, 2018
            \begin{itemize}
                \item We combine historical sales data with customer web activity to identify the potential for increased sales of the “long tail” products based on inventory reallocation and SKU rationalization.   
            \end{itemize}
        \item[--]MilliporeSigma: Pull-Through Revenue Potential of Fetal Bovine Serum, Spring, 2019
            \begin{itemize}
                \item We use historical sales data to investigate the relationship between low-margin FBS products and the other products and give the company suggestions on FBS stocking policies.   
            \end{itemize}
        \item[--]MilliporeSigma: Make-To-Stock Finished Item Selection, Fall, 2019
            \begin{itemize}
                \item We develop a decision supporting tool to help the company identify potential high-margin low-risk SKUs for make-to-stock.
            \end{itemize}
        \item[--]Belden: Price Optimization Model, Spring, 2020
            \begin{itemize}
                \item We develop a bidding price decision tool integrated with a SVM-based (support vector machine) demand prediction tool.
            \end{itemize}
        \item[--]Express Script: Drug Price Change Forecasts, Fall, 2020
            \begin{itemize}
                \item We develop a statistical learning model to forecast the drug price changes.
            \end{itemize}
        \item[--]Bunge: Demand and Supply Analysis on Lecithin, Spring, 2021
            \begin{itemize}
                \item We develop a parsimonious export and import flow model to characterize the lecithin demand and supply dynamics.
            \end{itemize}
    \end{itemize}

\section{OTHER}
    Programming Skills: Python, R, Matlab, Mathematica, {\it bash}, \LaTeX.\\
    Language: Mandarin (native), English.

\section{REFERENCES}
    {\bf Lingxiu Dong} 
    \newline Professor, Frahm Family Chair of Supply Chain, Operations, and Technology 
    \newline Olin Business School
    \newline Washington University in St. Louis
    \newline Email: dong@wustl.edu
    \newline Phone: (314) 935-6336\\
    ~
    \\
    {\bf Panos Kouvelis} 
    \newline Emerson Distinguished Professor of
    Supply Chain, Operations, and Technology
    \newline Director of Boeing Center on
    Technology, Information and Manufacturing
    \newline Olin Business School
    \newline Washington University in St. Louis
    \newline Email: kouvelis@wustl.edu
    \newline Phone: (314) 935-4604\\
    ~
    \\
    {\bf Jacob Feldman} 
    \newline Associate Professor of Supply Chain, Operations, and Technology
    \newline Olin Business School
    \newline Washington University in St. Louis
    \newline Email: jbfeldman@wustl.edu
    \newline Phone: (314) 935-4915\\
    ~
    \\
    {\bf Ren\'{e} Caldentey} 
    \newline Eli B. and Harriet B. Williams Professor of Operations Management
    \newline Booth School of Business
    \newline The University of Chicago
    \newline Email: rene.caldentey@chicagobooth.edu
    \newline Phone: (773) 702-4276\\

\end{resume}

\end{document}
